### 2014-03-07 src/methodology.Rnw
update

While the sampling criteria is simple, it is not immediately clear when we are faced with program elements that produced too few mutants for a particular fraction to yield at-least one mutant. For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(line, 1/64)} is less than 1. We analyzed the results of the following criterias: 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).

@@

A simple extension of this approach is to extend this strategy as previously, by choosing as many number of mutants as there are number of lines in a program element, and we can extend it as before to sample \textit{1/2,1/4,1/8,1/16,1/32,1/64} of the mutants thus chosen. We chose the rounding strategy for fractional samples for simplicity.

>>>>

While the sampling criteria is simple, it is not immediately clear when we are faced with program elements that produced too few mutants for a particular fraction to yield at-least one mutant. For example, for a line that produced 15 mutants, the number of mutants that can be chosen in \textit{(x\%, line, 1/64)} is less than 1. We analyzed the results of the following criterias: 1) to round the resulting number to the nearest integer, and choose that value as sampling (in effect, ignoring elements that are less complex), 2) to apply \textit{ceil} function to the resulting value, ensuring that there is atleast one mutant per program element, and 3) to perform the sampling in such a way that it chooses a mutant with with the fractional probability (this is the method followed by Zhang et al.~\cite{zhang2013ase}).

@@

A simple extension of this approach is to extend this strategy as previously, by choosing as many number of mutants as there are number of lines in a program element, and we can extend it as before to sample \textit{1/2,1/4,1/8,1/16,1/32,1/64} of the mutants thus chosen. We chose the rounding strategy for fractional samples for simplicity.
% TODO: Actually do the other rounding choices.

Here too, we have a few choices when sampling mutants. We could either choose the fraction of mutants within the program element, or we could apply the sampling externally. For example, using $\lambda_E$ as number of lines in an element, for \textit{(lpe, $1/2$, method)}, we first get $1/2 \times \lambda_{Method}$ number of mutants from each method. The second alternative is to get $\lambda_{Method}$ number of mutants for all methods, then from this larger set, choose only half of the mutants.
